\begin{thebibliography}{9}

\bibitem{rise-of-social-media}
Esteban Ortiz-Ospina. \textit{The rise of social media}. Available from: \url{https://ourworldindata.org/rise-of-social-media} [Accessed 24/05/2021]

\bibitem{pew-social-media-news-2018}
Pew Research Center. \textit{News Use Across Social Media Platforms 2018}. Available from: \url{https://www.journalism.org/2018/09/10/news-use-across-social-media-platforms-2018/} [Accessed 24/05/2021]

\bibitem{mbfc}
Media Bias/Fact Check. \textit{Media Bias/Fact Check}. Available from: \url{https://mediabiasfactcheck.com/} [Accessed 10/01/2021]

\bibitem{media-bias-chart}
Ad Fontes Media. \textit{Interactive Media Bias Chart}. Available from: \url{https://www.adfontesmedia.com/interactive-media-bias-chart-2/} [Accessed 10/01/2021]

\bibitem{yougov}
M. Smith. \textit{Left-wing vs right-wing: it’s complicated}. Available from: 
\url{https://yougov.co.uk/topics/politics/articles-reports/2019/08/13/left-wing-vs-right-wing-its-complicated} [Accessed 11/02/2021]

\bibitem{diffen}
Diffen. \textit{Left Wing vs Right Wing}. Available from: \url{https://www.diffen.com/difference/Left_Wing_vs_Right_Wing} [Accessed 11/02/2021]

\bibitem{MBFC-methodology}
Media Bias/Fact Check. \textit{Methodology}. Available from: \url{https://mediabiasfactcheck.com/methodology/} [Accessed 14/01/2021]

\bibitem{MBFC-CNN}
Media Bias Fact Check. \textit{CNN}. Available from: \url{https://mediabiasfactcheck.com/cnn/} [Accessed 14/01/2021]

\bibitem{baly-emnlp18}
R. Baly, G. Karadzhov, D. Alexandrov, J. Glass, P. Nakov. Predicting Factuality of Reporting and Bias of News Media Sources. \textit{Proceedings of the Conference on Empirical Methods in Natural Language Processing}, 2018. Available from: \url{https://arxiv.org/pdf/1810.01765v1.pdf} [Accessed 14/01/2021]

\bibitem{news-media-reliability}
R. Baly, G. Karadzhov, D. Alexandrov, J. Glass, P. Nakov. \textit{Factuality and Bias Prediction of News Media}. Available from: \url{https://github.com/ramybaly/News-Media-Reliability} [Accessed 14/01/2021]

\bibitem{word2vec}
T. Mikolov, K. Chen, G. Corrado, J. Dean. \textit{Efficient Estimation of Word Representations in Vector Space.} Available from: \url{https://arxiv.org/pdf/1301.3781.pdf} [Accessed 15/01/2021]

\bibitem{glove}
J. Pennington, R. Socher, C. Manning. \textit{GloVe: Global Vectors for Word Representation}. Available from: \url{https://nlp.stanford.edu/pubs/glove.pdf} [Accessed 15/01/2021]

\bibitem{gender-bias-word-embeddings}
T. Bolukbasi, K. Chang, J. Zou, V. Saligrama, A. Kalai. Man is to Computer Programmer as Woman is to
Homemaker? Debiasing Word Embeddings. \textit{30th Conference on Neural Information Processing Systems}, 2016. Available from: \url{https://arxiv.org/pdf/1607.06520v1.pdf} [Accessed 16/01/2021]

\bibitem{political-bias-word-embeddings}
J. Gordon, M. Babaeianjelodar, J. Matthews. Studying Political Bias via Word Embeddings. \textit{Companion Proceedings of the Web Conference}, 2020. Available from: \url{https://dl.acm.org/doi/pdf/10.1145/3366424.3383560} [Accessed 16/01/2021]

\bibitem{voong}
M. Voong, K. Gunda, SS. Gokhale. Predicting the Political Polarity of Tweets Using Supervised Machine Learning. \textit{IEEE 44th Annual Computers, Software, and Applications Conference}, 2020 Jul 13. p1707-1712. Available from: \url{https://ieeexplore.ieee.org/document/9202835} [Accessed 20/01/2021]

\bibitem{bert}
J. Devlin, M. Chang, K. Lee, K. Toutanova. \textit{BERT: Pre-training of Deep Bidirectional Transformers for Language Understanding}. arXiv preprint arXiv:1810.04805. 11th October 2018. Available from: \url{https://arxiv.org/pdf/1810.04805v2.pdf} [Accessed 17/01/2021]

\bibitem{chun}
S. Chun, R. Holowczak, K. Dharan, R. Wang, S. Basu, J. Geller. Detecting Political Bias Trolls in Twitter Data. \textit{Proceedings of the 15th International Conference on Web Information Systems and Technologies}, 2019. Available from: \url{https://www.scitepress.org/Link.aspx?doi=10.5220\%2f0008350303340342} [Accessed 17/01/2021]

\bibitem{bipartisan-press}
W. Wang. \textit{Calculating Political Bias and Fighting Partisanship with AI}. Available from: \url{https://www.thebipartisanpress.com/politics/calculating-political-bias-and-fighting-partisanship-with-ai/} [Accessed 17/02/2021]

\bibitem{roberta}
Y. Liu, M. Ott, N. Goyal, J. Du, M. Joshi, D. Chen, O. Levy, M. Lewis, L. Zettlemoyer, V. Stoyanov. \textit{RoBERTa: A Robustly Optimized BERT Pretraining Approach}. Available from: \url{https://arxiv.org/pdf/1907.11692.pdf} [Accessed 17/01/2021]

\bibitem{baly-acl2020}
R. Baly, G. Karadzhov, J. An, H. Kwak, Y. Dinkov, A. Ali, J. Glass, P. Nakov. What Was Written vs. Who Read It:
News Media Profiling Using Text Analysis and Social Media Context. \textit{Association for Computational Linguistics}, 2020. Available from: \url{https://arxiv.org/pdf/2005.04518v1.pdf} [Accessed 19/01/2021]

\bibitem{sattelberg}
W. Sattelberg. \textit{The Demographics Of Reddit: Who Uses The Site?}. Available from: \url{https://social.techjunkie.com/demographics-reddit/} [Accessed 21/01/2021]

\bibitem{reddit-api}
Reddit. \textit{Reddit API: Documentation}. Available from: \url{https://www.reddit.com/dev/api} [Accessed 07/05/21]

\bibitem{pushshift}
J. Baumgartner, S. Zannettou, B. Keegan, M. Squire, J. Blackburn. The PushShift Reddit dataset. \textit{Proceedings of the International AAAI Conference on Web and Social Media}, 6 May 2020 (Vol. 14, pp. 830-839). Available from: \url{https://arxiv.org/pdf/2001.08435v1.pdf} [Accessed 09/05/21]

\bibitem{praw}
B. Boe. \textit{PRAW: The Python Reddit API Wrapper}. Available from: \url{https://praw.readthedocs.io/en/latest/} [Accessed 30/05/2021]

\bibitem{lin}
K. Lin, C. Yang, H. Chen. What emotions do news articles trigger in their readers? \textit{Proceedings of the 30th annual international ACM SIGIR conference on research and development in information retrieval}, 2007. Available from: \url{https://dl.acm.org/doi/10.1145/1277741.1277882} [Accessed 19/01/2021]

\bibitem{ekman}
P. Ekman, R. Sorenson, W. Friesen. Pan-Cultural Elements in Facial Displays of Emotion. \textit{Science}, 1969. Volume 164, p. 86-88. Available from: \url{https://science.sciencemag.org/content/164/3875/86/tab-pdf} [Accessed 19/01/2021]

\bibitem{strapparava}
C. Strapparava, R. Mihalcea. SemEval-2007 Task 14: Affective Text. \textit{Proceedings of the Fourth International Workshop on Semantic Evaluations}, 2007. p70-74. Available from: \url{https://www.aclweb.org/anthology/S07-1013/} [Accessed 19/01/2021]

\bibitem{chien-tan}
C. Tan. Sentiment Analysis From the Reader’s Perspective [MEng Thesis]. Imperial College London. 2020.

\bibitem{garimella}
V. Garimella, I. Weber. A long-term analysis of polarization on Twitter. \textit{Proceedings of the International AAAI Conference on Web and Social Media}, 2017 May 3. Vol. 11, No. 1. Available from: \url{https://ojs.aaai.org/index.php/ICWSM/article/view/14918} [Accessed 20/01/2021]

\bibitem{rao}
D. Rao, D. Yarowsky, A. Shreevats, M. Gupta. Classifying latent user attributes in Twitter. \textit{Proceedings of the 2nd international workshop on Search and mining user-generated contents}, 2010. p37-44. Available from: \url{https://dl.acm.org/doi/abs/10.1145/1871985.1871993} [Accessed 20/01/2021]

\bibitem{kane}
B. Kane, J. Luo. Do the Communities We Choose Shape our Political Beliefs? A Study of the Politicization of Topics in Online Social Groups. \textit{IEEE International Conference on Big Data}, 2018 Dec 10. p3665-3671. Available from: \url{https://ieeexplore.ieee.org/document/8622535} [Accessed 20/01/2021]

\bibitem{massachs}
J. Massachs, C. Monti, G.D. Morales, F. Bonchi. Roots of Trumpism: Homophily and Social Feedback in Donald Trump Support on Reddit. \textit{12th ACM Conference on Web Science}, 6th July 2020. pp. 49-58. Available from: \url{https://dl.acm.org/doi/10.1145/3394231.3397894} [Accessed 25/05/2021]

\bibitem{ruder}
S. Ruder. \textit{Neural Transfer Learning for Natural Language Processing} (dissertaion). 2019. Available from: \url{https://ruder.io/thesis/neural_transfer_learning_for_nlp.pdf} [Accessed 19/05/2021]

\bibitem{pan-survey}
S.J. Pan, Q. Yang. A Survey on Transfer Learning. \textit{IEEE Transactions on Knowledge and Data Engineering}, 16th Oct 2009. Available from: \url{https://ieeexplore.ieee.org/document/5288526} [Accessed 19/05/2021]

\bibitem{daume}
H. Daumé III, D. Marcu. Domain adaptation for statistical classifiers. \textit{Journal of artificial Intelligence research}, 21st June 2006. Vol. 26, pp. 101-126. Available from: \url{https://arxiv.org/pdf/1109.6341.pdf} [Accessed 19/05/2021]

\bibitem{scl}
J. Blitzer, R. McDonald, F. Pereira. Domain adaptation with structural correspondence learning. \textit{Proceedings of the 2006 Conference on Empirical Methods in Natural Language Processing}, July 2006. pp. 120-128. Available from: \url{http://john.blitzer.com/papers/emnlp06.pdf} [Accessed 20/05/2021]

\bibitem{clker}
Clker. \textit{Free Clip Art \& Images}. Available from: \url{http://www.clker.com/} [Accessed 01/06/2021]

\bibitem{pan-sfa}
S.J. Pan, X. Ni, J.T. Sun, Q. Yang, Z. Chen. Cross-domain Sentiment Classification via Spectral Feature Alignment. \textit{Proceedings of the 19th International Conference on World Wide Web}, 26th April 2010. pp. 751-760. Available from: \url{https://dl.acm.org/doi/abs/10.1145/1772690.1772767} [Accessed 20/05/2021]

\bibitem{feature-adaptation}
L. Michelbacher, Q. Han, H. Schütze. Unsupervised Feature Adaptation for Cross-Domain NLP with an Application to Compositionality Grading. \textit{International Conference on Intelligent Text Processing and Computational Linguistics}, 24th March 2013. pp. 1-12. Springer, Berlin, Heidelberg. Available from: \url{https://rdcu.be/ckZ5Z} [Accessed 20/05/2021]

\bibitem{cdsc}
B. Myagmar, J. Li, S. Kimura. Cross-Domain Sentiment Classification with Bidirectional Contextualized Transformer Language Models. \textit{IEEE Access}, 8th November 2019. Vol. 7, pp. 163219-30. Available from: \url{https://ieeexplore.ieee.org/abstract/document/8894409} [Accessed 22/05/2021]

\bibitem{bert-feature-adaptation}
H. Ye, Q. Tan, R. He, J. Li, H.T. Ng, L. Bing. Feature Adaptation of Pre-Trained Language Models across Languages and Domains with Robust Self-Training. \textit{Proceedings of the 2020 Conference on Empirical Methods in Natural Language Processing (EMNLP)}, November 2020. pp. 7386-7399. Available from: \url{https://www.aclweb.org/anthology/2020.emnlp-main.599.pdf} [Accessed 23/05/2021]

\bibitem{domain-aware-bert}
C. Du, H. Sun, J. Wang, Q. Qi, J. Liao. Adversarial and Domain-Aware BERT for Cross-Domain Sentiment Analysis. \textit{Proceedings of the 58th Annual Meeting of the Association for Computational Linguistics}, July 2020. pp. 4019-4028. Available from: \url{https://www.aclweb.org/anthology/2020.acl-main.370/} [Accessed 23/05/2021]

\bibitem{adaptabert}
X. Han, J. Eisenstein. Unsupervised Domain Adaptation of Contextualized Embeddings for Sequence Labeling. arXiv preprint arXiv:1904.02817. 4th April 2019. Available from: \url{https://www.aclweb.org/anthology/D19-1433.pdf} [Accessed 23/05/2021]

\bibitem{dont-stop-pretraining}
S. Gururangan, A. Marasović, S. Swayamdipta, K. Lo, I. Beltagy, D. Downey, N.A. Smith. Don't Stop Pretraining: Adapt Language Models to Domains and Tasks. arXiv preprint arXiv:2004.10964. 23rd April 2020. Available from: \url{https://www.aclweb.org/anthology/2020.acl-main.740.pdf} [Accessed 23/05/2021]

\bibitem{sklearn}
F. Pedregosa, G. Varoquaux et al. \textit{scikit-learn}. Available from: \url{https://sklearn.org/} [Accessed 16/02/2021]

\bibitem{newsscraper}
J. Holwech, F. Shah. \textit{NewsScraper}. Available from: \url{https://github.com/fawazshah/NewsScraper} [Accessed 29/03/2021]

\bibitem{newspaper-python}
L. Ou-Yang. \textit{Newspaper3k: Article scraping \& curation}. Available from: \url{https://newspaper.readthedocs.io/en/latest/} [Accessed 29/03/2021]

\bibitem{nltk}
S. Bird, E. Loper, E. Klein. Natural Language Processing with Python. O’Reilly Media Inc. 2009.

\bibitem{wordnet}
Princeton University. \textit{About WordNet}. Available from: \url{https://wordnet.princeton.edu/}. [Accessed 29/03/2021]

\bibitem{adamw}
I. Loshchilov, F. Hutter. Decoupled weight decay regularization. 2017. Available from: \url{https://arxiv.org/pdf/1711.05101.pdf} [Accessed 29/03/2021]

\bibitem{russian-troll}
FiveThirtyEight. \textit{Russian Troll Tweets}. Available from: \url{https://github.com/fivethirtyeight/russian-troll-tweets/} [Accessed 06/04/21]

\bibitem{wordpiece}
Y. Wu, M. Schuster et al. Google's neural machine translation system: Bridging the gap between human and machine translation. 2016. Available from: \url{https://arxiv.org/pdf/1609.08144.pdf} [Accessed 08/04/21]

\bibitem{wordpiece-weaknesses}
R. Battle. \textit{Weaknesses of WordPiece Tokenization}. Available from: \url{https://medium.com/@rickbattle/weaknesses-of-wordpiece-tokenization-eb20e37fec99} [Accessed 25/05/2021]

\bibitem{ilyas}
I. Ilyas, X. Chu. \textit{Data Cleaning}. ACM Books. 2019.

\bibitem{guimaraes}
A. Guimaraes, O. Balalau, E. Terolli, G. Weikum. Analyzing the traits and anomalies of political discussions on Reddit. \textit{Proceedings of the International AAAI Conference on Web and Social Media}, 6th July 2019. Vol. 13, p. 205-213. Available from: \url{https://ojs.aaai.org/index.php/ICWSM/article/view/3222} [Accessed 10/05/21]

\bibitem{tyler}
C. Tyler. \textit{Reddit's leftward political bias}. Available from: \url{https://datainsights.pub/reddit_political_leanings/} [Accessed 14/05/21]

\bibitem{concept-drift}
J. Brownlee. \textit{A Gentle Introduction to Concept Drift in Machine Learning}. Available from: \url{https://machinelearningmastery.com/gentle-introduction-concept-drift-machine-learning/} [Accessed 17/05/21]

\bibitem{pushshift-problems}
D. Gaffney, J.N. Matias. Caveat Emptor, Computational Social Science: Large-Scale Missing Sata in a Widely-Published Reddit Corpus. \textit{PloS One}, 6th July 2018. 13(7):e0200162. Available from: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0200162} [Accessed 21/05/2021]

\bibitem{adaptabert-code}
X. Han, J. Eisenstein, F. Shah. \textit{Unsupervised Domain Adaptation of Contextualized Embeddings for Sequence Labeling}. Available from: \url{https://github.com/fawazshah/AdaptaBERT/} [Accessed 28/05/2021]

\bibitem{catastrophic-forgetting}
M. McCloskey, N.J. Cohen. Catastrophic Interference in Connectionist Networks: The Sequential Learning Problem. \textit{Psychology of Learning and Motivation}, 1st January 1989. Vol. 24, pp. 109-165. Academic Press. Available from: \url{https://www.sciencedirect.com/science/article/pii/S0079742108605368} [Accessed 06/06/2021]

\bibitem{conll}
E.F. Sang, F. De Meulder. Introduction to the CoNLL-2003 Shared Task: Language-Independent Named Entity Recognition. \textit{Proceedings of CoNLL-2003}, 12th June 2003, Edmonton, Canada. pp. 142-147. Available from: \url{https://arxiv.org/pdf/cs/0306050v1.pdf} [Accessed 04/06/2021]

\bibitem{reuters}
D. D. Lewis, Y. Yang, T. Rose, F. Li. \textit{RCV1: A New Benchmark Collection for Text Categorization Research}. \textit{Journal of Machine Learning Research}, 5:361-397, 2004. Available from: \url{http://www.jmlr.org/papers/volume5/lewis04a/lewis04a.pdf} [Accessed 04/06/2021]

\bibitem{wnut}
B. Strauss, B. Toma, A. Ritter, M.C. De Marneffe, W. Xu. Results of the WNUT16 Named Entity Recognition Shared Task. \textit{Proceedings of the 2nd Workshop on Noisy User-generated Text (WNUT)}, December 2016. pp. 138-144. Available from: \url{https://www.aclweb.org/anthology/W16-3919.pdf} [Accessed 04/06/2021]

\bibitem{dpa}
Data Protection Act 2018 (UK). Available from: \url{https://www.legislation.gov.uk/ukpga/2018/12/contents/enacted} [Accessed 21/01/2021]

\end{thebibliography}